Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2016-12-20 Manuscript/Manuscript.Rmd
added notes from meeting with SH

@@

>>>>

**Background notes from meeting with SH on Dec 20**
-CVD declining starting 1968 - see paper Ruel Stallones - cited in SH JAMA paper - history of decline in CVD.
-Richard cooper also written about BW diff in CVD with epi perspective
-for men there is stagnation from 1969 to late 1980s and then increase in gap with HIV and homicides
-massive crime wave in 1980s, black LE went down from 1984 to 1987 - period when both HIV and homicide went up -- the whole story during that time was HIV and homicide
-fundamentally interested in the qu is there a common story across most states or are there important differences in what happened in NY vs CA vs TX - can we say anything about what we know about state-specific policies, for example CA has strong anti-smoking legislation. Does this help us understand why the gap in Wisconsin was increasing?
-is there a lot of heterogeneity or is there not? - same something about the proportionate contribution by COD and by age - e.g., changes in injuries accounting for X% for closing the gap in NY but in AL it was Y%.
-heterogeneity between states in the contribution of the causes to the decline in the gap - maybe need to break up into at least two time periods with split at 1990.
-this is where the new figures come in which on the y-axis have the contribution to LE gap (in years or %) vs year on the x axis, and geom_line for each COD (do one COD at a time), and individual line for each state (may facet by census region).
-then have a view of how the different COD have contributed to the decline in the gap over time.

@@

**Figures 7 and 8 to be added: Trends in the contribution of CVD to the black-white life expectancy gap (in years) by US state**
-make one for males and one for females
-separately for each COD group
-included CIs
